Application-Level Regression Testing Framework using Jenkins

### 2017-03-05 manuscript/manuscript.tex
swtools and more

\section{Motivation}

\section{Jenkins Configuration}
\label{sec:JenkinsConfiguration}

\subsection{Introduction to Jenkins}
\subsection{Master-Node Configuration}
\subsection{Accessing Login Nodes}

@@

\subsection{Configuration Choices}
Jenkins instance was deployed on a vSphere managed VM running Centos 6.8. The VM allows restricted host-based ssh access from two secure OTP only administrative systems. The Jenkins GUI presented additional challenges. The Jenkins GUI is configured to log in as a standard user account with pass-wordless access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM. We restricting access to the physical VM and Jenkins GUI (bwjenkins) utilizing iptables, SSL and OTP.  A reverse proxy was used to run Jenkins behind apache/http with SSL for access to the administrative console. All the configuration is in /etc/httpd/config.d/ssl.conf. Anonymous access to the Jenkins GUI was allowed for limited read only view of test status and historical plots. The Anonymous access view is not restricted. \\
(config file snippets below)

@@

/etc/httpd/config.d/ssl.conf:
Listen 443
<VirtualHost _default_:443>
SSLSessionCache         shmcb:/var/cache/mod_ssl/scache
SSLSessionCacheTimeout  300
ServerName bwjenkins.ncsa.illinois.edu:443
 # -- The following sets ReverseProxy for Jenkins
  ProxyRequests       Off
  ProxyPreserveHost   On
  AllowEncodedSlashes On
  <Proxy *>
    Order deny,allow
    Allow from all
  </Proxy>
  ProxyPass       / http://localhost:8080/ nocanon
  ProxyPassReverse / http://localhost:8080/
  ProxyPassReverse / http://bwjenkins.ncsa.illinois.edu/
  RequestHeader set X-Forwarded-Proto "https"
  RequestHeader set X-Forwarded-Port "443"

@@

\subsection{LDAP with Jenkins}

\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{LDAP-Jenkins}
\caption{ Use LDAP with Jenkins }
\label{fig:LDAP-Jenkins}
\end{figure}

From the console view, select Manage Jenkins, select Configure Global Security. In the Security Realm section select the Advanced... tab. Input your LDAP server name and root DN. Click the Test Button.\\
\\
My first stab at this failed as an anonymous connection to our LDAP because we are using a local CA.
WARNING: Failed to search LDAP for username, 
sun.security.provider.certpath.SunCertPathBuilderException:
unable to find valid certification path to requested target\\
\\
Had to add our certificate to the keystore:
/usr/java/default/jre/bin/keytool -list -keystore cacerts -imle /etc/openldap/cacerts/cacert.pem
Enter keystore password: Trust this certificate? [no]:  yes\\
Certificate was added to keystore

@@

\section{SWTools Integration}
\label{sec:SWToolsIntegration}

@@

% references section

>>>>

\section{Motivation}
Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance. Another requirement was to find an automated solution for running a suite of test jobs that reveal the system health after upgrades and outages before returning the system to service.
\section{Jenkins Configuration}
\label{sec:JenkinsConfiguration}

\subsection{Introduction to Jenkins}
Jenkins [2] is a self-contained, open source automation server which can be used to automate all sorts of tasks such as building, testing, and deploying software. Jenkins can be installed through native system packages, Docker, or even run standalone by any machine with the Java Runtime Environment installed. 
To install from rpm as root:
wget -O /etc/yum.repos.d/jenkins.repo http://pkg.jenkins-ci.org/redhat/jenkins.repo
rpm --import https://jenkins-ci.org/redhat/jenkins-ci.org.key
yum install jenkins
\subsection{Master-Node Configuration}
We added a standard user account to our cluster that will execute the Jenkins tests. Unique ssh keys were generated on the Jenkins Server for accessing the user account on production and test environments.  The keys on the server are located in Jenkins home directory (/var/lib/jenkins/.ssh). Using the GUI management console, the keyfile location and passphrase was entered under Manage Jenkins, Configure System, SSH remote hosts section. A unique SSH site is configured for our TDS, production and development login nodes.

\subsection{Accessing Login Nodes}
The ssh public key generated on Jenkins Server was deployed in the login node user account. The login node sshd_config was modified to allow Public Key Authentication from the Jenkins Server IP.

@@

\subsection{Configuration Choices}
Jenkins instance was deployed on a vSphere managed VM running Centos 6.8. The VM allows restricted host-based ssh access from two secure OTP only administrative systems. The Jenkins GUI presented additional challenges. The Jenkins GUI is configured to log in as a standard user account with pass-wordless access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM. We restricting access to the physical VM and Jenkins GUI (bwjenkins) utilizing iptables, SSL and OTP.  A reverse proxy was used to run Jenkins behind apache/http with SSL for access to the administrative console. All the configuration is in /etc/httpd/conf.d/ssl.conf. Anonymous access to the Jenkins GUI was allowed for limited read only view of test status and historical plots. The Anonymous access view is not restricted. \\
(config file snippets below)

@@

/etc/httpd/conf.d/ssl.conf:
Listen 443
<VirtualHost _default_:443>
SSLSessionCache         shmcb:/var/cache/mod_ssl/scache
SSLSessionCacheTimeout  300
ServerName bwjenkins.ncsa.illinois.edu:443
 # -- The following sets ReverseProxy for Jenkins
  ProxyRequests       Off
  ProxyPreserveHost   On
  AllowEncodedSlashes On
  <Proxy *>
    Order deny,allow
    Allow from all
  </Proxy>
  ProxyPass       / http://localhost:8080/ nocanon
  ProxyPassReverse / http://localhost:8080/
  ProxyPassReverse / http://bwjenkins.ncsa.illinois.edu/
  RequestHeader set X-Forwarded-Proto "https"
  RequestHeader set X-Forwarded-Port "443"

@@

\subsection{LDAP with Jenkins}
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{LDAP-Jenkins}
\caption{ Use LDAP with Jenkins }
\label{fig:LDAP-Jenkins}
\end{figure}
To enable LDAP, the LDAP Plugin was installed. To configure, from the console view, select Manage Jenkins, select Configure Global Security. In the Security Realm section select the Advanced... tab. Input your LDAP server name and root DN. Click the Test Button.\\
\\
My first stab at this failed as an anonymous connection to our LDAP because we are using a local CA.
WARNING: Failed to search LDAP for username, 
sun.security.provider.certpath.SunCertPathBuilderException:
unable to find valid certification path to requested target\\
\\
Had to add our certificate to the keystore:
/usr/java/default/jre/bin/keytool -list -keystore cacerts -imle /etc/openldap/cacerts/cacert.pem
Enter keystore password: Trust this certificate? [no]:  yes\\
Certificate was added to keystore

@@

\section{SWTools Integration}
\label{sec:SWToolsIntegration}
\subsection{SWTools with Jenkins}
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{swtools-Jenkins}
\caption{ Use SWTools with Jenkins }
\label{fig:swtools-jenkins}
\end{figure}

\subsection{SWTools with Lammps}
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{swtools-lammps-jenkins}
\caption{ SWTools with Lammps }
\label{fig:swtools-lammps-jenkins}
\end{figure}

@@

% references section
\section*{References}
[1] http://inca.sdsc.edu/ Inca Monitoring: periodic, automated, user-level cyberinfrastructure testing
[2] https://jenkins.io/ Jenkins: open source automation server written in Java
